Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-05-28 JCB/results_JCB.tex
res 16s

To simulate sequencing error in the sequence of interest,
 we use the the next-generation sequencing read simulator 
ART~\cite{huang2012art}. The Illumina technology main error mode is base substitution. We used
this model since those
are the errors that \RNApyro detects. As parameters, the reads reads generated
were $75\text{bps}$ long for an average fold coverage of $5$, $10$ and $15$. 
 They yield respectively an average error rate of $2.4\%$, $0.9\%$ and $0.6\%$.

 As in Sec.~\ref{sec:5S} we used a value of $\beta=15$ and evaluated $\alpha$ at $0, 0.5, 0.8, 1.0$. 
 Additionally since the alignment still contains gap, we made sure to evaluate the isostericity term

>>>>

To simulate sequencing error in the sequence of interest,
 we use the the next-generation sequencing read simulator 
ART~\cite{huang2012art}. The Illumina technology main error mode is base substitution. We used
this model since those
are the errors that \RNApyro detects. As parameters, the reads  generated
were $75\text{bps}$ long for an average fold coverage of $5$, $10$ and $15$. 
 They yield respectively an average error rate of $2.4\%$, $0.9\%$ and $0.6\%$.

We used a value of $\beta=15$ and evaluated $\alpha$ at $0, 0.5, 0.8, 1.0$. 
 Additionally since the alignment still contains gap, we made sure to evaluate the isostericity 
 term only
 with sequences in the MSA where both positions in the base pair are not gaps. 
 Due to the low number of errors, we set the presumed as twice the average error rate made by ART, i.e. $4.8\%$, $1.8\%$ and $1.2\%$ for fold coverages of $5$, $10$ and $15$ respectively.

To evaluate our method, we simulated with a random sequences from the MSA every time,
 $12$ times the $5-$fold, $10$ times the $10-$fold and $14$ times the $15-$fold coverage. And we 
 evaluated the ROC curve as in Sec.~\ref{sec:5S}.
